Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-30 LaTeX/paper.tex
Formatting for arxiv
Add notes for adjustment

% -*- Mode:TeX -*-
% LaTeX template for CinC papers                   v 1.1a 22 August 2010
%
% To use this template successfully, you must have downloaded and unpacked:
%       http://www.cinc.org/authors_kit/papers/latex.tar.gz
% or the same package in zip format:
%       http://www.cinc.org/authors_kit/papers/latex.zip
% See the README included in this package for instructions.
%
% If you have questions, comments or suggestions about this file, please
% send me a note!  George Moody (george@mit.edu)
%
\documentclass[twocolumn]{cinc}
\usepackage{graphicx}
\usepackage{dblfloatfix}
\begin{document}
\bibliographystyle{cinc}

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, Toffoli gates (otherwise known as NOT, or X gates) are applied on 
  $R_z[0]$ and $R_z[1]$, so that states where $R_z=|001111\rangle$ will temporarily be in
  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
  will apply only for the desired states. These operations are then performed again,
  returning all but the target qubit (which has the Z-gate applied) to their original
  states.

>>>>

% -*- Mode:TeX -*-
% LaTeX template for CinC papers                   v 1.1a 22 August 2010
%
% To use this template successfully, you must have downloaded and unpacked:
%       http://www.cinc.org/authors_kit/papers/latex.tar.gz
% or the same package in zip format:
%       http://www.cinc.org/authors_kit/papers/latex.zip
% See the README included in this package for instructions.
%
% If you have questions, comments or suggestions about this file, please
% send me a note!  George Moody (george@mit.edu)
%
\documentclass[twocolumn]{cinc}
\usepackage{graphicx}
\usepackage{dblfloatfix}
\usepackage{url}
\begin{document}
\bibliographystyle{cinc}

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
  so that states where $R_z=|001111\rangle$ will temporarily be in
  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
  will apply only for the desired states. These operations are then performed again,
  returning all but the target qubit (which has the Z-gate applied) to their original
  states.
